---
title: "Homework 1"
author: "Shelley Shen"
date: 09-15-2020
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following is my solution to Homework 1.

```{r}
library(tidyverse)
```


# Question 1

Creating a data frame with the specified elements:

```{r}
prob1_df = tibble(
  samp = rnorm(10), 
  samp_gt_0 = samp > 0, 
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("high", "mod", "low", "high", "mod", "low", "high", "mod", "low", "low"))
  )
```

Finding the mean of each variable in the data frame: 

```{r warning = FALSE}
  mean(pull(prob1_df, samp))
  mean(pull(prob1_df, samp_gt_0))
  mean(pull(prob1_df, char_vec))
  mean(pull(prob1_df, factor_vec))
```
  I was able to successfully take the mean of variables that are logical and numeric (samp and samp_gt_0) but not of the character and factor vector variables (char_vec and factor_vec). 


Converting the vectors to another type: 

```{r}
  as.numeric(pull(prob1_df, samp))
  as.numeric(pull(prob1_df, samp_gt_0))
  as.numeric(pull(prob1_df, char_vec))
  as.numeric(pull(prob1_df, factor_vec))
```


# Question 2:

Load penguins dataset: 

```{r}
data("penguins", package = "palmerpenguins")
```

**Description of penguins dataset:**

Names and values of important variables in dataset: 
```{r}
  ls(penguins)
  print(penguins)
```

Size of dataset:

The penguins dataset has __`r nrow(penguins)`__ rows and __`r ncol(penguins)`__ columns. 


*Finding the mean flipper length in mm:*

Convert all values in the variable flipper_length_mm into numeric variables: 
```{r}
  as.numeric(pull(penguins, flipper_length_mm))
```

Finding, recoding, and omitting missing values: 
```{r}
  sum(is.na(penguins))
  penguins$flipper_length_mm[penguins$flipper_length_mm == 99] <- NA
  na.omit(penguins)
```

Calculate the mean of flipper lengths: 
```{r}
  mean(pull(penguins, flipper_length_mm))
  mean(penguins, na.rm=TRUE)
```

summary(penguins)

The mean flipper length of the penguins dataset is `r mean(penguins, flipper_length_mm)`


*Scatterplot of flipper length vs. bill length:*
```{r warning = FALSE}
  ggplot(penguins, aes(x = bill_depth_mm, y = flipper_length_mm, color = species)) + geom_point()
```

