---
title: "Homework 1"
author: "Shelley Shen"
date: 09/18/2020
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following is my solution to Homework 1.

```{r}
library(tidyverse)
library(palmerpenguins)
```


# Question 1

Creating a data frame with the specified elements:

```{r}
prob1_df = tibble(
  samp = rnorm(10), 
  samp_gt_0 = samp > 0, 
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "low", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Finding the mean of each variable in the data frame: 

```{r warning = FALSE}
  mean(pull(prob1_df, samp))
  mean(pull(prob1_df, samp_gt_0))
  mean(pull(prob1_df, char_vec))
  mean(pull(prob1_df, factor_vec))
```
  I was able to successfully take the mean of variables that are logical and numeric (samp and samp_gt_0), but not of the character and factor vector variables (char_vec and factor_vec). 


Converting the vectors to another type: 

```{r eval = FALSE}
  as.numeric(pull(prob1_df, samp)) 
  as.numeric(pull(prob1_df, samp_gt_0))
  as.numeric(pull(prob1_df, char_vec))
  as.numeric(pull(prob1_df, factor_vec))
```
  I could successfully convert the logical and factor variables to numeric, however I could not convert the character variable to a numeric type. 
  The logical variables of samp and samp_gt_0 can be converted to numeric because theyre're logical and numeric. The factor variable has levels so a numeric value can be assigned. However, the character variable does not have any levels or logic so a numeric value cannot be assigned to the vector. 
  
  The mean can be calculated for logical and numeric vectors but not for character and factor vectors because they do not have a numeric value. 
  
  
```{r}
  as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
  as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
  as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

  The result of the conversion of the logical vector to a factor then multiplied by the random sample is not meaningful because when the variable becomes a factor vector, arithmetic functions are not applicable. 

# Question 2

```{r}
data("penguins", package = "palmerpenguins")
```

```{r}
  summary(penguins)
  view(penguins)
```


_Description of penguins dataset:_



    The sample size of the dataset is `r nrow(penguins)` penguins.
    The dataset has __`r nrow(penguins)`__ rows and __`r ncol(penguins)`__ columns. 
    The categories of variables in the penguin dataset are `r names(penguins)`. 
    The species of penguins in the dataset are `r levels(pull(penguins, "species"))`, and they live on the islands of `r levels(pull(penguins,     "island"))`. 
        The mean flipper length of the penguins in the dataset is __`r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`__ mm. 


## Scatterplot of flipper length (mm) vs. bill length (mm)
```{r warning = FALSE}
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
  ggsave("penguins_scatterplot.pdf", height = 4, width = 6)
```

