---
title: "Homework 1"
author: "Shelley Shen"
date: 09/19/2020
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following is my solution to Homework 1.

```{r}
library(tidyverse)
```


# Question 1

*Creating a data frame with the specified elements:*

```{r}
prob1_df = tibble(
  samp = rnorm(10), 
  samp_gt_0 = samp > 0, 
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "low", "mod", "mod", "mod", "high", "high", "high"))
  )
```

*Finding the mean of each variable in the data frame:*

```{r collapse = TRUE, warning = FALSE}
  mean(pull(prob1_df, samp))
  mean(pull(prob1_df, samp_gt_0))
  mean(pull(prob1_df, char_vec))
  mean(pull(prob1_df, factor_vec))
```
I was able to successfully take the mean of variables that are logical and numeric (samp and samp_gt_0), but not of the character and factor vector variables (char_vec and factor_vec). 


*Converting the vectors to numeric type:*

```{r collapse = TRUE, eval = FALSE}
  as.numeric(pull(prob1_df, samp)) 
  as.numeric(pull(prob1_df, samp_gt_0))
  as.numeric(pull(prob1_df, char_vec))
  as.numeric(pull(prob1_df, factor_vec))
```
I could successfully convert the logical and factor variables to numeric, however I could not convert the character variable to a numeric type. The logical variables of samp and samp_gt_0 can be converted to numeric because they're logical and numeric. The factor variable has levels so a numeric value can be assigned in order of the level. However, the character variable does not have any levels or logic so R cannot coerce the variable and a numeric value cannot be assigned to the vector. 
  
The result of this conversion helps to explain why earlier, the mean could be calculated for logical and numeric vectors but not for the character vector.  
  
*Converting the vectors to another type:*

```{r collapse = TRUE, warning = FALSE}
  as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
  as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
  as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

The result of the conversion of the logical vector to a factor then multiplied by the random sample is not meaningful because when the variable becomes a factor vector, arithmetic functions are not applicable. 

# Question 2

```{r echo = FALSE}
  library(palmerpenguins)
```

```{r echo = FALSE}
data("penguins", package = "palmerpenguins")
```

*Description of penguins dataset:*

```{r eval = FALSE}
  summary(penguins)
  view(penguins)
```

The sample size of the dataset is `r nrow(penguins)` penguins.
The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
    
The penguins dataset collected information on `r ncol(penguins)` variables, and those variables are `r names(penguins)`. 
The three species of penguins in the dataset are `r levels(pull(penguins, "species"))`, and they live on the islands of `r levels(pull(penguins, "island"))`. 

The bill length ranges from `r min(pull(penguins, bill_length_mm), na.rm = TRUE)` mm to `r max(pull(penguins, bill_length_mm), na.rm = TRUE)` mm.
The bill depth ranges from `r min(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm to `r max(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm. 
The flipper length ranges from `r min(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm to `r max(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. 
The average body mass of penguins is `r mean(pull(penguins, body_mass_g), na.rm = TRUE)` g. 
The number of female penguins vs. male penguins in the dataset is as follows: `r table(pull(penguins, sex))`. 

The mean flipper length of the penguins in the dataset is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. 


## Scatterplot of flipper length (mm) vs. bill length (mm)
```{r echo = FALSE, warning = FALSE}
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
  ggsave("penguins_scatterplot.pdf", height = 4, width = 6)
```
